|

### 2024-08-08 doc/paper.qmd
table 1
pickle output path

## delete or take fikirs below
```{python}
#| echo: false
#| output: false

import pickle

with open('../output/results.pickle', 'rb') as f:
        results = pickle.load(f)

min_fyear, max_fyear, no_unique_firms = results['Desc information'].values()

def rename_var_to_label(table, italic=True):
    for var_name, var_label in results['Variable Names'].items():
        var_label = f'\\textit{{{var_label}}}' if italic else var_label
        table = table.replace(var_name, var_label)
    return table
```

## from fikir
```{python}
#| echo: false
#| output: false

@@

with open('../output/results.pickle', 'rb') as f:
        results = pickle.load(f)

@@

>>>>

```{python}
#| echo: false
#| output: false

@@

with open('data/generated/table_1.pickle', 'rb') as f:
    results = pickle.load(f)

@@

print(prep_latex_table(
    results['table_1'],
    caption='Table 1: Number of Firm-Year Observations per Country',
    label='tab:table_1'
))
```
